Supplemental Appendix for ``Out-of-Sample Comparisons of Overfit Models''

### 2014-09-22 appendix.tex
Correct stupid spelling mistake in title of appendix
Minor tweaks to paper

\title{Supplamental Appendix for ``Out-of-Sample Comparisons of
  Overfit Models''}
\author{Gray Calhoun\thanks{email: \protect\url{gcalhoun@iastate.edu}} \\
  Iowa State University}

@@

\begin{figure}\centering
  {\large Coverage of recursive DMW OOS interval in simulations}
  \input{floats/mc-interval-generror1-rec.tex}
  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
    a one-sided interval based on the recursive DMW \oost\ test,
    plotted as a function of the fraction of observations used in the
    test sample, $P/T$.  The solid horizontal line denotes the
    intervals' nominal coverage.}
  \label{fig:interval-T}
\end{figure}

>>>>

\title{Supplemental Appendix for ``Out-of-Sample Comparisons of
  Overfit Models''}
\author{Gray Calhoun\thanks{email: \protect\url{gcalhoun@iastate.edu}} \\
  Iowa State University}

@@

\begin{figure}[b]\centering
  {\large Coverage of recursive DMW OOS interval in simulations}
  \input{floats/mc-interval-generror1-rec.tex}
  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
    a one-sided interval based on the recursive DMW \oost\ test,
    plotted as a function of the fraction of observations used in the
    test sample, $P/T$.  The solid horizontal line denotes the
    intervals' nominal coverage.}
  \label{fig:interval-T}
\end{figure}
